\chapter{Preface}

I have always believed that research is inherently a collaborative effort. Ideas are rarely born in a split second of epiphany, but are more often shaped and crystallized incrementally over many, sometimes heated, discussions with peers. My experience in doing the work that led to this thesis has confirmed this belief. This thesis would not have been possible without the contributions and support of many people. First and foremost I would like to thank my supervisors, Guus Schreiber, Lora Aroyo, and Jacco van Ossenbruggen. Guus you offered me enough freedom to find my way and fulfill my potential as a researcher. Your insight in defining the overarching goals of this thesis was instrumental and your guidance during the overall research process was invaluable. I would like to thank Lora for her many excellent ideas and suggestions. Her tireless collaboration with various stakeholders such as the Netherlands Institute for Sound and Vision and several dutch broadcasters greatly contributed to the success of this work. Thank you Jacco for your most valuable contributions and suggestions to both the research and writing process. Many times when I was facing a difficult decision I relied on your judgment which was almost always right.

I would also like to thank Michiel Hildebrand which acted as my forth unofficial supervisor. He joined the Vrije Universiteit Amsterdam as a postdoctoral researched at the end of the first year of my PhD studies. As a recent PhD graduate, he was able to provide a perspective on what it means to be a PhD researcher that resonated with me.  This was rather fortunate as I was  just at beginning my journey. His suggestions and advice helped to shape many of the results in this work.

Many thanks to Davide Ceolin and Valentina Maccatrozzo Ceolin who were fellow PhD students and are dear friends. We spent many moments together sharing the joy and the occasional torments which are inseparable part of the journey of every PhD student. Your support and friendship are greatly appreciated.

My thanks also to Zarko Aleksovski who was one of my supervisors during my internship at Philips  Research. During this period I got acquainted with the area of Semantic Web and had the pleasure to briefly work with Frank van Harmelen. This experience was the main factor that led me to pursue a PhD in this area. I would also like to thank Jasen Markovski for recommending me for the internship position and many thanks to Dragan Sekulovski for being a great company.

I would like to express special thanks to my dear friend Balthasar Schopman. We worked together for more than two years and his sense of humor and positive outlook on life were a great addition to the working environment. I find his uncompromising attitude towards things that matter to him most admirable.

Special thanks to Ognen Lukas and Daniela Remenska, dear friends with whom I spent many great moments together. They were big	 and very important part of my life outside of academia.
 
I would also like to thank all colleagues from the \textit{Web and Media} and \textit{Knowledge Representation and Reasoning groups} which I have not mentioned by name here. The discussions and the exchange of ideas during the various meetings and the encounters in the coffee corners were an essential driving force in my work.

Last but not least, I would like to express profound gratitude to my family. To my parents Spomenka and Kole who have sacrificed a great deal to provide me with opportunities and without their endless support and guidance through life I would not be where I am now. To my sister Gonca and her family for always being there for me. To my in-laws Lidija, Emilija and Dragan who have supported me tremendously over the years. And to my beloved Irina and daughter Sofija who are my source of joy and inspiration.